\bibliographystyle{agsm}
%\bibliography{ref}

%\begin{thebibliography}{xx}
%
%\bibitem[1]{Besters2016}
%Besters, L.~M., van Ours, J.~C. \harvardand\ van Tuijl, M.~A.  \harvardyearleft
%  2016\harvardyearright , `Effectiveness of in-season manager changes in
%  english premier league football', {\em De Economist} {\bf 164}(3),~335--356.
%
%\bibitem[2]{bruinshoofd_terWell_2003}
%Buinsfold, A. \harvardand\ ter Weel, B.  \harvardyearleft 2003\harvardyearright
%  , `Manager to go? performance dips reconsidered with evidence from dutch
%  football', {\em European Journal of Operational Research} {\bf 148}(2),~233
%  -- 246.
%
%\bibitem[3]{Chawla_etal_2002}
%Chawla, N.~V., Bowyer, K.~W., Hall, L.~O. \harvardand\ Kegelmeyer, W.~P.
%  \harvardyearleft 2002\harvardyearright , `Smote: Synthetic minority
%  over-sampling technique', {\em Journal of Artificial Intelligence Research}
%  {\bf 16}(1),~321--357.
%
%\bibitem[4]{elliott_lieli_2013}
%Elliott, G. \harvardand\ Lieli, R.~P.  \harvardyearleft 2013\harvardyearright ,
%  `Predicting binary outcomes', {\em Journal of Econometrics} {\bf 174}(1),~15
%  -- 26.
%
%
%\bibitem[5]{Hastie_Tibshirani}
%Hastie, T. \harvardand\ Tibshirani, R.  \harvardyearleft 2016\harvardyearright
%  , {\em The Elements of Statistical Learning: Data Mining, Inference, and
%  Prediction}, second edn, Springer.
%
%\bibitem[6]{Hastie_LASSO}
%Hastie, T., Tibshirani, R. \harvardand\ Wainwright, M.  \harvardyearleft
%  2015\harvardyearright , {\em Statistical Learning with Sparsity: The Lasso
%  and Generalizations}, Chapman \& Hall/CRC.
%
%\bibitem[7]{Hastie_ISLR}
%James, G., Witten, D., Hastie, T. \harvardand\ Tibshirani, R.  \harvardyearleft
%  2014\harvardyearright , {\em An Introduction to Statistical Learning: With
%  Applications in R}, Springer.
%\newline\harvardurl{http://www-bcf.usc.edu/~gareth/ISL/}
%
%
%
%
%\end{thebibliography}




%\bibliographystyle{IEEEtrans}
%\bibliography{ref}
\begin{thebibliography}{}

\harvarditem{Ajay~Agrawal \harvardand\ Gans}{2018}{agrawal_etal_book}
Ajay~Agrawal, A.~G. \harvardand\ Gans, J.  \harvardyearleft
  2018\harvardyearright , {\em Prediction Machines: The Simple Economics of
  Artificial Intelligence}, Harvard Business Review Press.

\harvarditem{Baltagi}{2013}{baltagi_panel_textbook}
Baltagi, B.~H.  \harvardyearleft 2013\harvardyearright , {\em Econometrics of
  Panel Data}, Wiley.

\harvarditem{Gelman \harvardand\ Rubin}{2018}{gelman_etal_book}
Gelman, Andrew, J. B. C. H. S. S. D. B. D. A.~V. \harvardand\ Rubin, D.~B.
  \harvardyearleft 2018\harvardyearright , {\em Bayesian Data Analysis}, third
  edn, CRC Press.
\newline\harvardurl{http://www.stat.columbia.edu/~gelman/book}

\harvarditem{Hennekens~CH}{1996}{hennekens_etal_1996}
Hennekens~CH, Buring~JE, M. J. S. M. R. B. C. N. B. C. L. F. G. J. R. P. W. W.
  P.~R.  \harvardyearleft 1996\harvardyearright , `Lack of effect of long-term
  supplementation with beta-carotene on the incidence of malignant neoplasms
  and cardiovascular disease.', {\em New England Journal of Medicine} {\bf
  334}(18),~1145--1149.

\harvarditem{Kuhn \harvardand\ Johnson}{2019}{kuhn_johnson_feature}
Kuhn, M. \harvardand\ Johnson, K.  \harvardyearleft 2019\harvardyearright ,
  {\em Feature Engineering and Selection: A Practical Approach for Predictive
  Models}, Chapman and Hall/CRC.

\harvarditem{Pafka}{2019}{pafka_benchmark}
Pafka, S.  \harvardyearleft 2019\harvardyearright , `benchm-ml'.
\newline\harvardurl{github.com/szilard/benchm-ml}

\harvarditem{Sally \harvardand\ Anderson}{2013}{anderson_sally}
Sally, D. \harvardand\ Anderson, C.  \harvardyearleft 2013\harvardyearright ,
  {\em The Numbers Game: Why Everything You Know About Soccer Is Wrong},
  Viking/Penguin, New York.

\harvarditem{Salsburg}{2001}{salsburg_lady}
Salsburg, D.  \harvardyearleft 2001\harvardyearright , {\em The Lady tasting
  tea}, Henry Holt and Co.

\harvarditem{Shen}{2017}{shen_airlines}
Shen, Y.  \harvardyearleft 2017\harvardyearright , `{Market competition and
  market price: Evidence from United/Continental airline merger}', {\em
  Economics of Transportation} {\bf 10}(C),~\hbox{1--7}.

\harvarditem{Wooldridge}{2001}{wooldridge_advanced}
Wooldridge, J.  \harvardyearleft 2001\harvardyearright , {\em Econometric
  Analysis of Cross Section and Panel Data}, The MIT Press.

\end{thebibliography}



\bibliographystyle{harvard}
%\bibliography{ref}

\begin{thebibliography}{}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Ajay~Agrawal og Gans(2018)]{agrawal_etal_book}
\textbf{Ajay~Agrawal og Gans}, \textbf{2018}.
\newblock Avi~Goldfarb Ajay~Agrawal og Joshua Gans.
\newblock \textit{Prediction Machines: The Simple Economics of Artificial
  Intelligence}.
\newblock Harvard Business Review Press, 2018.

\bibitem[Gelman og Rubin(2018)]{gelman_etal_book}
\textbf{Gelman og Rubin}, \textbf{2018}.
\newblock John B. Carlin Hal S. Stern David B. Dunson Aki~Vehtari Gelman,
  Andrew og Donald~B. Rubin.
\newblock \textit{Bayesian Data Analysis}.
\newblock CRC Press, third edition, 2018.
\newblock URL \url{http://www.stat.columbia.edu/~gelman/book}.

\bibitem[Sally og Anderson(2013)]{anderson_sally}
\textbf{Sally og Anderson}, \textbf{Jun 2013}.
\newblock David Sally og Chris Anderson.
\newblock \textit{The Numbers Game: Why Everything You Know About Soccer Is
  Wrong}.
\newblock Viking/Penguin, New York, 2013.

\bibitem[Wooldridge(2001)]{wooldridge_advanced}
\textbf{Wooldridge}, \textbf{2001}.
\newblock Jeffrey Wooldridge.
\newblock \textit{Econometric Analysis of Cross Section and Panel Data}.
\newblock The MIT Press, 2001.

\end{thebibliography}


%%IEEEtrans.bst

\bibliographystyle{IEEEtrans}

\begin{thebibliography}{}

\bibitem{AbGr18}
S.~{Abenda and P. G. Grinevich}.
\newblock {Rational degeneration of M-curves, totally positive Grassmannians
  and KP2-solitons}.
\newblock {\em Commun. Math. Phys.}, 361:1029--1081, 2018.

\bibitem{AbGr19}
S.~{Abenda and P. G. Grinevich}.
\newblock {Reducible M-curves for Le-networks in the totally-nonnegative
  Grassmannian and KP-II multiline solitons}.
\newblock {\em Selecta Math.}, 25:43, 2019.

\bibitem{AS_1977}
M.~J. Ablowitz and H.~Segur.
\newblock Exact linearization of a {Painlev\'e transcendent}.
\newblock {\em Phys. Rev. Lett.}, 38(20):1103--1106, 1977.

\bibitem{AC_1991}
M.~J. {Ablowitz and P. A. Clarkson}.
\newblock {\em Solitons, Nonlinear Evolution Equations and Inverse Scattering},
  volume 149 of {\em London Mathematical Society Lecture Note Series}.
\newblock Cambridge University Press, 1991.

\bibitem{AKNS}
M.~{Ablowitz, D. J. Kaup, A. C. Newell and H. Segur}.
\newblock The inverse scattering transform-{F}ourier analysis for nonlinear
  problems.
\newblock {\em Studies in Appl. Math.}, 53(4):249--315, 1974.

\bibitem{AbMa}
R.~Abraham and J.~Marsden.
\newblock {\em Foundations of Mechanics}.
\newblock AMS Chelsea Publishing, Providence, Rhode Island, 2nd edition, 2008.


\bibitem{ZJZ}
P.~Zinn-Justin and J.-B. Zuber.
\newblock {On some integrals over the U(N) unitary group and their large N
  limit}.
\newblock {\em J. Phys. A: Math. Gen.}, 36:3173--3193, 2003.

\bibitem{Zo}
P.~Zograf.
\newblock {Enumeration} of {Gr\"othendieck's dessins and KP hierarchy}.
\newblock {\em Int. Math. Res. Notice}, 24:13533--13544, 2015.

\bibitem{Zvonkin97}
A.~Zvonkin.
\newblock Matrix integrals and map enumeration: an accessible introduction.
\newblock {\em Math. Comput. Modelling}, 26(8-10):281--304, 1997.
\newblock Combinatorics and Physics (Marseille, 1995).

\end{thebibliography}
